Cross-sectoral conservation of the Indian Ocean

### 2022-02-23 Msc_Thesis_Lea_v2.Rmd
Update Msc_Thesis_Lea_v2.Rmd
Added cons_feats tibble

+ Active + inactive vents: 70% [.csv to .shp](https://datacarpentry.org/r-raster-vector-geospatial/10-vector-csv-to-shapefile-in-r/) [dataset  datum](https://vents-data.interridge.org/sites/vents-data.interridge.org/files/InterRidge_Vents_Database_Version3.1_documentation.pdf)
+ Seamounts: 30% (but some advocate for more: Letessier et al., 2019, PLOS Biology)
+ Plateaus: >30%

@@

@@

```
p_ConsFeat <- problem(PUs, features = ConsFeatures, cost_column = "NoCost") %>% 
  add_min_set_objective() %>%
  add_relative_targets(ConsFeatures$amount) %>% # representation targets (Area)
  add_binary_decisions() %>%
  add_lpsymphony_solver(verbose = FALSE) #%>%

>>>>

+ Active + inactive vents: 70% [.csv to .shp](https://datacarpentry.org/r-raster-vector-geospatial/10-vector-csv-to-shapefile-in-r/) [dataset  datum](https://vents-data.interridge.org/sites/vents-data.interridge.org/files/InterRidge_Vents_Database_Version3.1_documentation.pdf)
+ Seamounts: 30% (but some advocate for more: Letessier et al., 2019, PLOS Biology)
+ Plateaus: 30%

@@

Cons_feats <- tibble(Features = c("IBA", "IMMA", "NEIO_09", "NWIO_14", "SIO_11", "SIO_19", "SIO_22", "SIO_23", "SIO_30", "SIO_32", "SIO_35", "SIO_36", "SIO_37","Seamounts", "Plateaus", "Active_Vents", "Inactive_Vents"), Targets = c(0.3, 0.3, 0.3, 0.3, 0.3, 0.7, 0.7, 0.7, 0.7, 0.7, 0.7, 0.7, 0.7, 0.3, 0.3, 0.7, 0.7))

@@

*Code based on Alvise's work, not as code here to avoid issues when knitting*

```
p_ConsFeats <- problem(PUs, Cons_feats$Features, cost_column = "NoCost") %>%
  add_min_set_objective() %>%
  add_relative_targets(Cons_Feats$Targets) %>% #
  add_binary_decisions() %>%
  add_lpsymphony_solver(verbose = FALSE) #%>%
